Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-07 tex/sections/apm.tex
Update resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    verifies that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept$ flag. More formally it evaluates $(H',accept)=P(H,
    R_{good})$, where $H'$ is the updated heap chunks and the $accept$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and the $accept$ flag is set
    to false if a request execution completes normally.
    \item \textbf{Postprocessor:} This module is responsible for calculating the updated commitments
    $(\mathbf{C}_{H'}, \mathbf{C}_{P'})$ and the final $\mathbf{accept}$ flag. Installing new applications or
    updating the code of existing application is performed by this module.
\end{itemize}

>>>>

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    verifies that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept_N$ flag. More formally it evaluates $(H',accept_N)=P(H,
    R_{good})$, where $H'$ is the updated heap chunks and the $accept_N$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept_F=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and the $accept_F$ flag is set
    to false if a request execution completes normally.

    The FRU has a higher circuit complexity than the NEU\@. Unlike the NEU, the FRU is able to restore the initial state
    of the heap when an application fails. It also calculates the execution cost of every instruction and if the
    application's execution cost exceeds its predefined cap, the FRU will terminate the application.
    \item \textbf{Postprocessor:} This module is responsible for calculating the updated commitments
    $(\mathbf{C}_{H'}, \mathbf{C}_{P'})$ and the final $\mathbf{accept}$ flag. Installing new applications or
    updating the code of existing application is performed by this module.
\end{itemize}

### 2022-09-07 tex/sections/blocks.tex
Update resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In summary, a validator validates a block by verifying three computation proofs: $\pi_{\tau}$ which proves the
transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and $\pi_{h-q}$
which proves the previous block has a correct certificate of validators. It should be noted that these proofs are not
a part of the block contents.

>>>>

In summary, a validator validates a block by verifying three computation proofs: $\pi_{\tau}$ which proves the
transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and $\pi_{h-1}$
which proves the previous block has a correct certificate of validators. It should be noted that these proofs are not
a part of the block contents.

### 2022-09-07 tex/sections/consensus.tex
Update resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The credibility of a block of the Argennon blockchain is determined by the certificates it has received
from different sets of users, known as committees. There are two primary type of certificate committees in
Argennon: the committee of \emph{delegates} and the committee
of \emph{validators}. Argennon has \emph{one} committee of delegates and $m$ committees of validators.

The committee of delegates issues a certificate for every block of the Argennon blockchain, and each
committee of validators issues a certificate every $m$ blocks. A validators' committee will
certify a block only if it has already been certified by the committee of delegates. Every committee of validators has
an index between $0$ and $m - 1$, and it issues a certificate for block number $n$, if $n$ modulo $m$ equals
the committee index.

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the committee of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

@@

A block certificate issued by some members of a validators' committee is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:\footnote{If we calculate
the stake values based on the previous block a malicious committee can select the validators of the next block.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the committee is higher than \texttt{minOnlineStake} fraction
    of the total stake of the committee. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the committee members that have \texttt{online} status.
\end{itemize}

@@

As we mentioned before, the block with height $n$ needs a certificate from the committee of
validators with index $n$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committee. An honest validator never signs a certificate for two different blocks with the
same height.

@@

block certificates issued by committees of validators are included in the blocks of the Argennon blockchain.
A block can contain multiple certificates, provided that
those certificates belong to consecutive blocks.

>>>>

The credibility of a block of the Argennon blockchain is determined by the certificates it has received
from different sets of users, known as committees. There are two primary type of certificate committees in
Argennon: the committee of \emph{delegates} and the assembly of \emph{validators}. Argennon has \emph{one} committee
of delegates and $m$ assemblies of validators.

The committee of delegates issues a certificate for every block of the Argennon blockchain, and each
assembly of validators issues a certificate every $m$ blocks. A validators assembly will
certify a block only if it has already been certified by the committee of delegates. Every assembly of validators has
an index between $0$ and $m - 1$, and it issues a certificate for block number $n$, if $n$ modulo $m$ equals
the assembly index.

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the assembly of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

@@

A block certificate issued by some members of a validators assembly is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:\footnote{If we calculate
the stake values based on the previous block a malicious committee can select the validators of the next block.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the committee is higher than \texttt{minOnlineStake} fraction
    of the total stake of the committee. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the committee members that have \texttt{online} status.
\end{itemize}

@@

As we mentioned before, the block with height $n$ needs a certificate from the assembly of
validators with index $n$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committee. An honest validator never signs a certificate for two different blocks with the
same height.

@@

block certificates issued by validators assemblies are included in the blocks of the Argennon blockchain.
A block can contain multiple certificates, provided that
those certificates belong to consecutive blocks.

### 2022-09-07 tex/sections/elements.tex
Update resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An Argennon application or smart contract is an HTTP server which is represented by an Argennon Standard
Representation (ASR) and whose state is stored in the Argennon blockchain. Each Argennon application is identified by
a unique application identifier.

@@

\section{Transactions}\label{sec:transactions}

An Argennon transaction consist of an HTTP request made by a user to an Argennon application, a resource
declaration object and a list of signed messages. Transactions can only be
issued by users and applications can not create transactions. An Argennon transaction is also called
an \emph{external request}.

@@

>>>>

An Argennon application or smart contract is an HTTP server which is represented by an Argennon Standard Application
Representation (ASAR) and whose state is stored in the Argennon blockchain. Each Argennon application is identified by
a unique application identifier.

@@

\section{External Requests}\label{sec:transactions}

An Argennon \emph{external request} (i.e.\ transaction) consist of an HTTP request made by a user to an Argennon application, a
resource declaration object and a list of signed messages. External requests can only be
issued by users and requests created by applications are called \emph{internal request}.

@@

\section{Resource Management}\label{sec:res-man}

Completing an execution session requires computational resources. The amount of resources used by an execution session
should be monitored and managed, otherwise a malicious user would be able to easily spam and exhaust resources of the
execution environment.

In most consensus protocols, we can assume that the block proposer has enough incentive to filter out transactions
that spam run-time resources. Here by a run-time resource, we mean a resource that at run-time, a limited amount
of it is available, but its surplus can not be stored for later use. Execution time and local memory are
examples of such a resource but permanent storage is not.

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In the Argennon protocol the management of run-time resources, is left to the block proposer.

In Argennon the reference for resource usage is the Argennon Prover Machine. The APM has two different execution
units: the NEU which is used for executing external requests that the block proposer claims will complete
successfully and the FRU which executes requests that the proposer has classified as failed requests. The FRU has a
more restricted resource management and less resources are available for requests that use the FRU.

We recall from Section~\ref{ch:APM} that the APM configuration is a tuple:
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}).
\]
When requests are executed by the APM, the following run-time resources should be considered:

\begin{itemize}
    \item \textbf{execution cost}:
    each APM instruction has a protocol defined cost and the execution cost of a program can be calculated
    deterministically. Only the FRU performs these calculations and verifies that an external request does not exceed
    its predeclared execution cost.

    For executing all request of a block, at max, The NEU will run for
    $\mathcal{T}_{\text{NEU}}$ steps and the FRU will run for
    $\mathcal{T}_{\text{FRU}}$ steps.

    \item \textbf{local memory}: $\mathcal{L}_{\text{NEU}}, \mathcal{L}_{\text{FRU}}$. The Argennon protocol requires
    $\mathcal{L}_{\text{NEU}} = 3\mathcal{L}_{\text{FRU}}$, so the NEU has three times more local memory.

    \item \textbf{stack size}: both the FPU and the NEU has the same stack size: $\mathcal{S}$

    \item \textbf{heap access list}:
    every session can only access heap locations that are declared in its access list. In addition,
    resizing heap chunks can only be done in the range of the pre-declared lower bound and upper bound. Both the NEU
    and the FRU enforce this restriction.
    \item \textbf{app access list}:
    a session may only make requests to applications that are declared in its application access list. Both the NEU
    and the FRU enforce this restriction.
    \item \textbf{call depth}:
    during a session the number of nested application calls can not be more than a threshold. This threshold is
    determined by the Argennon protocol. It should be noted that a differed call is considered like a normal call and
    increases the call depth by one level. Only the FRU enforces this restriction.
\end{itemize}

In Argennon the proposer does not use the APM for executing requests and directly executes the ASAR of an
application, which is much more efficient. Only when he wants to reject a transaction because of excessive resource
usage, he will emulate the APM to make sure that the request will be rejected by the FRU. The differences between the
NEU and FRU ensures that this policy is safe.
